Proof-Reconstruction in Type Theory for Propositional Logic

### 2017-10-22 paper/sections/proof-reconstruction.tex
changes definitions
[ paper ] last changes.

% \begin{functiondef}{$\fuh_{0}$ : \Prop → \Prop}
%   \label{eq:uh-definition}

% \begin{array}
%     &\fuh_{0} &&: \Prop → \Prop\\
%     &\fuh_{0}\ (φ₁ ⇒ (φ₂ ⇒ φ₃)) &&= \fuh_{0}((φ₁ ∧ φ₂) ⇒ φ₃)\\
%     &\fuh_{0}\ (φ₁ ⇒ (φ₂ ∧ φ₃)) &&= \fuh_{0}(φ₁ ⇒ φ₂) ∧ \fuh_{0}(φ₁ ⇒ φ₃)\\
%     &\fuh_{0}\ φ &&= φ
% \end{array}

% \end{functiondef}

@@

\begin{align}
  \label{eq:uh-structured}
  \begin{split}
    &\fuh_{1} : \Prop → \Nat \to \Prop\\
    &\fuh_{1}(φ, \zero)\hspace{3mm}= φ\\%\hspace{10cm}\\
    &\fuh_{1}(φ, \suc(n)) =\\
    &\hspace{3mm}\begin{cases}
    \fuh_{1}((φ₁ ∧ φ₂) ⇒ φ₃, n),
      &\text{ if } φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\[2mm]
    \fuh_{1}(φ₁ ⇒ φ₂, n)\\
    ∧\ \fuh_{1}(φ₁ ⇒ φ₃, n),
       &\text{ if } φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃).
  \end{cases}
  \end{split}
\end{align}

@@

\begin{align*}
  \begin{split}
  % \label{eq:rank-definition}
    &\frank : \Prop → \Nat\\
    &\frank(φ) =
    \begin{cases}
    \frank(φ₁) + c_{¬},  &\text{ if } φ ≡ \neg φ₁ \\
    \fmax{(\frank(φ₁),\ \frank(φ₂))} + c_{\square},
      &\text{ if } φ ≡ φ₁\,\square\, φ₂.\\
    0, &\text{ otherwise}
    \end{cases}
  \end{split}
\end{align*}

@@

\begin{align*}
  \begin{split}
      &\fuh_{cm} : \Prop → \Nat\\
      &\fuh_{cm}(φ) =\\
      &\hspace{3mm}
        \begin{cases}
        \fuh_{cm}(φ₃) + 2, &\text{ if }φ ≡ φ₁ ⇒ (φ₂ ⇒ φ₃)\\
        \fmax(\fuh_{cm}(φ₂),\ \fuh_{cm}(φ₃)) + 1,
          &\text{ if }  φ ≡ φ₁ ⇒ (φ₂ ∧ φ₃)\\
        0, &\text{ otherwise.}
        \end{cases}
  \end{split}
\end{align*}

@@

\begin{definition}[uh]
  \label{def:uh}
    \begin{align}
      \label{eq:uh}
      \begin{split}
      &\fuh : \Prop → \Prop\\
      &\fuh(φ) = \fuh_{1}(φ, \fuh_{cm}(φ)).
      \end{split}
    \end{align}
\end{definition}

>>>>

\begin{equation*}
\label{eq:uh-definition}
\begin{aligned}
&\hspace{.495mm}\fuh_{0} : \Prop → \Prop\\
&\begin{array}{lll}
  \fuh_{0} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{0}((φ₁ ∧ φ₂) ⇒ φ₃)\\
  \fuh_{0} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fuh_{0}(φ₁ ⇒ φ₂) ∧ \fuh_{0}(φ₁ ⇒ φ₃)\\
  \fuh_{0} &φ                &= φ
\end{array}
\end{aligned}
\end{equation*}

@@

\begin{equation}
\label{eq:uh-structured}
\begin{aligned}
&\hspace{.495mm} \fuh_{1} : \Prop → \Nat \to \Prop\\
&\begin{array}{llll}
\fuh_{1} &(φ₁ ⇒ (φ₂ ⇒ φ₃)) &(\suc~n) &= \fuh_{1}~((φ₁ ∧ φ₂) ⇒ φ₃)~n\\
\fuh_{1} &(φ₁ ⇒ (φ₂ ∧ φ₃)) &(\suc~n) &= \fuh_{1}~(φ₁ ⇒ φ₂)~n ∧ \fuh_{1}~(φ₁ ⇒ φ₃)~n\\
\fuh_{1} &φ &\xspace\emph{n} &= φ
\end{array}
\end{aligned}
\end{equation}

@@

\begin{equation}
% \label{eq:rank-definition}
\begin{aligned}
&\hspace{.495mm}\frank : \Prop → \Nat\\
&\begin{array}{llll}
\frank~(¬~φ)           &= \frank~φ₁~+~c_{¬}\\
\frank~(φ₁~\square~φ₂) &= \fmax~(\frank~φ₁)~(\frank~φ₂) + c_{\square}\\
\frank~φ               &= 0
\end{array}
\end{aligned}
\end{equation}

@@

\begin{equation*}
% \label{eq:rank-definition}
\begin{aligned}
&\hspace{.495mm}\fuh_{cm} : \Prop → \Nat\\
&\begin{array}{llll}
\fuh_{cm}~(φ₁ ⇒ (φ₂ ⇒ φ₃)) &= \fuh_{cm}(φ₃) + 2\\
\fuh_{cm}~(φ₁ ⇒ (φ₂ ∧ φ₃)) &= \fmax~(\fuh_{cm}~φ₂)~(\fuh_{cm}~φ₃) + 1\\
\fuh_{cm}~φ                &= 0
\end{array}
\end{aligned}
\end{equation*}

@@

\begin{align}
  \label{eq:uh}
  \begin{split}
  &\fuh : \Prop → \Prop\\
  &\fuh(φ) = \fuh_{1}(φ, \fuh_{cm}(φ)).
  \end{split}
\end{align}
